Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-23 paper/HH4b.tex
Done with corrections
Completed revision of paper

\abstract{
  The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  We study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mis-identification, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy against the
  effects of pile-up.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ channel
alone could allow for the observation of double Higgs production
  at the High Luminosity LHC.
}

@@

\bibliography{HH4b}

>>>>

\abstract{
  The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  We study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mis-identification, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy in
  a high pile-up environment.
  %
  For an integrated luminosity of $\mathcal{L}=3000~(300)$ fb$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 7.2~(2.3)$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ final state
alone could allow for the discovery of double Higgs production
at the High Luminosity LHC.
%
We also find that, provided light and charm
jet mis-identification can be reduced, observation of
Higgs pairs in the $b\bar{b}b\bar{b}$ final state could
be within reach already at Run II.
}

@@

%\bibliography{HH4b}
\input{HH4b.bbl}

### 2015-12-23 paper/sec-analysis.tex
Completed revision of paper

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} consists of eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.
%
From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
jet clustering.

In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
%
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with transverse momentum less than 5\% of the transverse momentum of the large-$R$ jet are removed.
%
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
which is particularly susceptible
to soft, wide-angle contaminations.
%
No trimming is applied to the small-$R$ jets.

To validate the subtraction of PU,
we compare representative kinematic distributions
without PU, with PU, and with PU after the combined
application of {\tt SoftKiller} and trimming (SK+Trim).
%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of the
Higgs candidates for signal
events in the resolved and boosted categories.
%
If PU is not subtracted there is a large shift in the Higgs mass
peak, by about 40 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of $\simeq 5$ GeV
and a broadening of the mass
distribution.
%
For the boosted category, we find that
the mass distributions for jets to which no trimming
is applied peaks at around 160~GeV, even
after PU subtraction with {\tt SoftKiller}.
%
When trimming is applied in addition to {\tt SoftKiller}, 
the distribution peaks close to the nominal Higgs mass.

@@

In Fig.~\ref{fig:mHH_PU}
we compare the transverse momentum of the leading Higgs
candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
$m_{hh}$, in both the boosted and resolved categories.
%
In the case of the $p_T^{h_1}$ distribution, the differences between the selection
criteria for the resolved
and boosted categories is reflected in the rightward shift of the latter.
%
The effect of PU is small in the boosted case, and generally moderate
in the resolved case, except for at large $p_T$.
%
A similar behaviour is observed in the di-Higgs invariant mass distribution.
%
Therefore we can consider the PU subtraction strategy
as validated for the purposes of this study, although
further optimisation should still be possible.

@@

We can also assess the impact of PU in some of
substructure variables that will be 
used as input to the MVA in the boosted category.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions, $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
%
Comparing the signal distributions in the cases without PU and
with PU subtracted with SK, we observe that
the shapes of both substructure variables
are reasonably robust in a environment including PU.
%

@@

It is also interesting to quantify how
the relative differences between
signal over background distributions are modified by the inclusion of PU.
%
Considering the boosted category initially,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematic distributions for signal and background events,
with and without PU for the leading Higgs candidate: the invariant mass, the transverse
momentum distribution $p_T$,
     the 2--to--1 subjettiness ratio $\tau_{21}$, and 
     the $k_T$ splitting scale $\sqrt{d_{12}}$.
     %
      We verify that the relevant
      qualitative differences between signal
      and background distributions are maintained  in the presence of PU.
      %
      This is especially noticeable for the substructure variables, which
      exhibit a similar discriminatory power both with and without
      PU.

@@

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
Again, the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

To complete this discussion, it is illustrative to determine
the mass resolution obtained for the
reconstructed Higgs candidates in the various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\delta m_h$, %as well as the
and the corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
%
        We find a mass resolution of around 9 GeV in the case
        without PU, which worsens only slightly
        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
        with SK subtraction.
        %
        We also note that after subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[h]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        \multicolumn{4}{|c|}{Resolved category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
          & subleading Higgs   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
        \hline
          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
          & subleading Higgs   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
          \hline
            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
          & subleading Higgs   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
            \hline
            \multicolumn{4}{c}{}\\
             \hline
        \multicolumn{4}{|c|}{Boosted category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
          & subleading Higgs   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
        \hline
              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading Higgs  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
          & subleading Higgs   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved (upper table)
        and boosted (categories) category.
        %
        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction (only for resolved),
        and the same with SK(+Trim) subtraction.
        %
        We indicate the shift of the invariant
        mass peak $\la m_h^{\rm reco}\ra$ as compared
        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
        for both the leading and subleading Higgs candidates.
      }
    \end{table}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Cacciari:2008gd,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} consists of eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.

From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
jet clustering.

In addition, jet trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to large-$R$ jets.
%
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$ subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with transverse momentum less than 5\% of the total
transverse momentum of the large-$R$ jet are then removed.
%
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
which is particularly susceptible
to soft, wide-angle contaminations.
%
No trimming is applied to the small-$R$ jets.

@@

%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of the
Higgs candidates for signal
events in the resolved and boosted categories.
%
 In the resolved category,
    we compare  the results without PU
    with those with PU $\la n_{\rm PU}\ra=80$,
    with and without SK subtraction.
    %
    If PU is not subtracted, there is a large shift in the Higgs mass
peak, by more than 30 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of $\simeq 5$ GeV
and a broadening of the mass
distribution.
    %
    In the boosted case, the comparison is performed between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
%
We find that
the mass distribution for jets to which no trimming
is applied peaks at around 160~GeV, even
after PU subtraction with {\tt SoftKiller}.
%
When trimming is applied in addition to {\tt SoftKiller}, 
the distribution peaks close to the nominal Higgs mass.

In Fig.~\ref{fig:mHH_PU}
we compare the transverse momentum of the leading Higgs
candidate, $p_t^{h}$ and the invariant mass of the di-Higgs system
$m_{hh}$, in both the boosted and resolved categories.
%
In the case of the $p_T^{h}$ distribution, the differences between the selection
criteria for the resolved
and boosted categories is reflected in the rightward shift of the latter.
%
After subtraction,
the effects of PU are small in the two categories.
%
A similar behaviour is observed in the di-Higgs invariant mass distribution.
%
We can also assess the impact of PU in some of
substructure variables that will be 
used as input to the MVA in the boosted category.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions, $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
%
We observe that
the shapes of both substructure variables
are reasonably robust in a environment including PU.
%
Therefore we can consider the PU subtraction strategy
as validated for the purposes of this study, although
further optimisation should still be possible, both
for the trimming and for the {\tt SoftKiller}
input settings.

@@

@@

It is also interesting to quantify how
the relative differences between
signal over background distributions are modified by the inclusion of PU.
%
Considering the boosted category initially,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematic distributions for signal and background events,
with and without PU for the leading Higgs candidate: the transverse
momentum distribution $p_T$,
the $p_T$ of the leading AKT03 subjet,
     the 2--to--1 subjettiness ratio $\tau_{21}$, and 
     the $k_T$ splitting scale $\sqrt{d_{12}}$.
     %
      We verify that the relevant
      qualitative differences between signal
      and background distributions are maintained  in the presence of PU.
      %
      This is especially noticeable for the substructure variables, which
      exhibit a similar discriminatory power both with and without
      PU.

@@

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
with and without PU, for the invariant mass and the
transverse momentum of the leading
     Higgs candidate.
     %
     Again, the PU-subtracted background distributions
     appear reasonably close
     to their counterparts without PU, and thus
     the distinctive features between signal and background
     are maintained after PU subtraction.

@@

It is illustrative to determine
the mass resolution obtained for the
reconstructed Higgs candidates in the various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\la m_h^{\rm reco}\ra-m_h$,
and the corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction (only for the
        resolved category), and the same with SK(+Trim) subtraction.

        In both categories,
        we find a mass resolution of around 9 GeV in the case
        without PU.
        %
        In the case of PU
        with SK(+Trim) subtraction,
        in the resolved category the mass resolution
        worsens only slightly
        to around 11 GeV, while in the boosted category we find
        the same resolution as in the no PU case.
        %
        We also note that after SK(+Trim) subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[t]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        \multicolumn{4}{|c|}{Resolved category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading $h$  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
          & subleading $h$   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
        \hline
          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading $h$  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
          & subleading $h$   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
          \hline
            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading $h$  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
          & subleading $h$   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
            \hline
            \multicolumn{4}{c}{}\\
             \hline
        \multicolumn{4}{|c|}{Boosted category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading $h$  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
          & subleading $h$   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
        \hline
              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading $h$  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
          & subleading $h$   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved (upper table)
        and boosted (categories) category.
        %
        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction (only for resolved),
        and the same with SK(+Trim) subtraction.
        %
        We indicate the shift of the invariant
        mass peak $\la m_h^{\rm reco}\ra$ as compared
        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
        for both the leading and subleading Higgs candidates.
      }
    \end{table}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-23 paper/sec-conclusions.tex
Completed revision of paper

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
all relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of the $4b$ process,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant pileup.

Combining the contributions from the resolved,
intermediate and boosted categories, we find that, for
$\mathcal{L}=3$ ab$^{-1}$, the
signal significance for
the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 4.0$.
%
This indicates that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim evidence for Higgs pair production at
the HL-LHC.
%
Our study also suggests possible avenues that the LHC experiments
could explore to further improve this signal significance.
%
One handle would be to reduce the contribution from light and charm
jet mis-identification, ensuring that the irreducible $4b$ background 
 dominates over the $2b2j$ component.
%
Another possibility would be to improve the mass resolution of the Higgs
reconstruction
in high-PU environments, and, more in general,
to optimize the PU subtraction
strategy in order
to reduce the impact of PU in the modelling
of kinematical variables and the associated
degradation in the MVA discrimination.
%
Such experimental improvements might
even make
an observation of Higgs pair production possible at the
end of Run II with
$\mathcal{L}=300$ fb$^{-1}$.

One important implication of this work is that it should
be possible to improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach is however
rather
non-trivial, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare with the corresponding  precision 
that has been reported from other final states such as
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$.
%
It will also be  interesting to perform
this exercise for a 100 TeV hadron collider~\cite{Barr:2014sga,
  Azatov:2015oxa,Papaefstathiou:2015iba,
  Arkani-Hamed:2015vfh}.
%
While signal yields will be certainly increased, also the (gluon-driven) QCD
multijet background will grow strongly.
%
Revisiting
the present analysis, including the MVA optimization,
at 100 TeV will allow us
to assess the accuracy of an extraction of the trilinear
coupling $\lambda$ from the $b\bar{b}b\bar{b}$ final state
at 100 TeV.

@@

{\bf\noindent  Acknowledgments \\}
We thank F.~Bishara, R.~Contino, A.~Papaefstathiou and
G.~Salam for useful discussions on the topic
of Higgs pair production.
%
We thank E.~Vryonidou and M.~Zaro for
assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.
%
  J.~R. is supported by an STFC Rutherford Fellowship and
  Grant ST/K005227/1 and ST/M003787/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant ``PDF4BSM".
%
K.~B. is supported by a Rhodes Scholarship.
%
D.~B., J.~F. and C.~I. are supported by the STFC.

>>>>

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the LHC.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
all relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of the $4b$ process,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant pile-up.

Combining the contributions from the resolved,
intermediate and boosted categories, we find that, for
$\mathcal{L}=3$ ab$^{-1}$, the
signal significance for
the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 7$.
%
This indicates that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim discovery of Higgs pair production at
the HL-LHC.
%
Our study also suggests possible avenues that the LHC experiments
could explore to further improve this signal significance.
%
One handle would be to reduce the contribution from light and charm
jet mis-identification, ensuring that the irreducible $4b$ background 
 dominates over the $2b2j$ component.
%
Another possibility would be to improve the mass resolution of the Higgs
reconstruction
in high-PU environments, and, more in general,
to optimize the PU subtraction
strategy in order
to reduce the impact of PU in the modelling
of kinematical variables and the associated
degradation in the MVA discrimination.
%
Such experimental improvements might
even make possible
an observation of Higgs pair production at the
end of Run II with
$\mathcal{L}=300$ fb$^{-1}$.

Another challenging aspect of the measurement of Higgs pairs
in the $b\bar{b}b\bar{b}$ final state is achieving an efficient
triggering strategy.
%
In order to reduce the rate from background QCD processes sufficiently, while
being able
to access the relevant $p_T$ regimes, (multi-)jet triggers
using $b$-quark tagging information online for one or more jets are
likely to be
necessary.
%
The additional rejection provided by these triggers could
enable events to be selected efficiently, with four
jets down to $p_T=45$ GeV in the resolved category,
and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
$p_T=200$ GeV.

One important implication of this work is that it should
be possible to significantly
improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach is however
rather
non-trivial, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare with the corresponding  precision 
that has been reported from other final states such as
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$.
%
It will also be  interesting to perform
this exercise for a 100 TeV hadron collider~\cite{Barr:2014sga,
  Azatov:2015oxa,Papaefstathiou:2015iba,
  Arkani-Hamed:2015vfh}.
%
While at 100 TeV the
signal yields would be increased, also the (gluon-driven) QCD
multijet background would grow strongly.
%
Revisiting
the present analysis, including the MVA optimization,
at 100 TeV would also allow
to assess the accuracy of an extraction of the trilinear
coupling $\lambda$ from the $b\bar{b}b\bar{b}$ final state
at 100 TeV.

@@

{\bf\noindent  Acknowledgments \\}
We thank F.~Bishara, R.~Contino, A.~Papaefstathiou and
G.~Salam for useful discussions on the topic
of Higgs pair production.
%
We thank E.~Vryonidou and M.~Zaro for
assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.

  \noindent
  The work of K.~B. is supported by a Rhodes Scholarship.
  %
  D.~B., J.~F. and C.~I. are supported by the STFC.
  %
  J.~R. and N.~H. are
supported by an European Research Council Starting Grant ``PDF4BSM".
%
  J.~R. is supported by an STFC Rutherford Fellowship and
  Grant ST/K005227/1 and ST/M003787/1.
